\vspace{-2.25cm} Development of Ocular Disease Auxiliary Diagnosis System

### 2024-08-27 Paper/Paper.tex
Import tables into latex

\documentclass{article}
\usepackage{ctex}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{caption}
\RequirePackage{longtable,multirow,array}
\RequirePackage{booktabs}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[style=ieee,sorting=nyt]{biblatex}
\assignrefcontextentries[]{*}
\addbibresource{References.bib}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\hypersetup{hidelinks}
\hypersetup{bookmarksnumbered=true,
	bookmarksopen=true,
	colorlinks=true,
	linkcolor=black,
	citecolor=blue,
	urlcolor=black}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{mhchem}
\pgfplotsset{compat=1.18}
\captionsetup{justification=centering}
\captionsetup[figure]{name={Fig.},labelsep=space,labelfont=bf}
\captionsetup[table]{name={Table},labelsep=space,labelfont=bf}
\CTEXoptions[today=old, contentsname=Contents]
\newcommand{\authyear}[1]{\citeauthor{#1} (\citeyear{#1})}
\setmainfont{Arial}

@@

@@

			Table: for each disease:
				precision
				recall/sensitivity
				specificity
				F1
				AUC
			Graph: D1 acc bar chart (with D2 no use-top-probs and D2 use-top-probs)
			Graph: D1 confusion matrix
			TEXT: comments

>>>>

\documentclass{article}
\usepackage{ctex}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{caption}
\RequirePackage{longtable,multirow,array}
\RequirePackage{booktabs}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[style=ieee,sorting=nyt]{biblatex}
\assignrefcontextentries[]{*}
\addbibresource{References.bib}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\hypersetup{hidelinks}
\hypersetup{bookmarksnumbered=true,
	bookmarksopen=true,
	colorlinks=true,
	linkcolor=black,
	citecolor=blue,
	urlcolor=black}
\usepackage{tikz}
\usepackage{pgfplotstable}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\captionsetup{justification=centering}
\captionsetup[figure]{name={Fig.},labelsep=space,labelfont=bf}
\captionsetup[table]{name={Table},labelsep=space,labelfont=bf}
\CTEXoptions[today=old, contentsname=Contents]
\newcommand{\authyear}[1]{\citeauthor{#1} (\citeyear{#1})}
\setmainfont{Arial}

@@

				\begin{table}[htbp]
					\centering
					\caption{OCT Test}
					\label{tb:OCT_test}
					\pgfplotstabletypeset[
						multicolumn names,
						col sep=comma,
						columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
						columns/Abnormity/.style={string type, column name=Abnormities},
						columns/Precision/.style={string type, column name=Precision},
						columns/Sensitivity/.style={string type, column name=Sensitivity},
						columns/Specificity/.style={string type, column name=Specificity},
						columns/FOne/.style={string type, column name={F1 Score}},
						columns/AUC/.style={string type, column name=AUC},
						every head row/.style={before row=\toprule, after row=\midrule},
						every last row/.style={ after row=\bottomrule}
					]{Tables/abnormity_o_test.csv}
				\end{table}

				\begin{table}[htbp]
					\centering
					\caption{Fundus Test}
					\label{tb:Fundus_test}
					\pgfplotstabletypeset[
					multicolumn names,
					col sep=comma,
					columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
					columns/Abnormity/.style={string type, column name=Abnormities},
					columns/Precision/.style={string type, column name=Precision},
					columns/Sensitivity/.style={string type, column name=Sensitivity},
					columns/Specificity/.style={string type, column name=Specificity},
					columns/FOne/.style={string type, column name={F1 Score}},
					columns/AUC/.style={string type, column name=AUC},
					every head row/.style={before row=\toprule, after row=\midrule},
					every last row/.style={after row=\bottomrule}
					]{Tables/abnormity_f_test.csv}
				\end{table}

@@

			\begin{table}[htbp]
				\centering
				\caption{Diagnosis Test}
				\label{tb:diagnosis_test}
				\pgfplotstabletypeset[
				multicolumn names,
				col sep=comma,
				columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
				columns/Abnormity/.style={string type, column name=Abnormities},
				columns/Precision/.style={string type, column name=Precision},
				columns/Sensitivity/.style={string type, column name=Sensitivity},
				columns/Specificity/.style={string type, column name=Specificity},
				columns/FOne/.style={string type, column name={F1 Score}},
				columns/AUC/.style={string type, column name=AUC},
				every head row/.style={before row=\toprule, after row=\midrule},
				every last row/.style={ after row=\bottomrule}
				]{Tables/diagnosis2.csv}
			\end{table}

			Graph: D1 acc bar chart (with D2 no use-top-probs and D2 use-top-probs)
			Graph: D1 confusion matrix
			TEXT: comments
